---
title: "Homework 6"
author: "Anusorn Thanataveerat"
date: "November 15, 2018"
output: github_document
toc: true
toc_float: true
code_folding: hide
---

```{r setup, include=FALSE}
library(tidyverse)
library(janitor)
library(knitr)
library(broom)
library(lubridate)

knitr::opts_chunk$set(echo = TRUE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
```

## Problem 1

``` {r Problem_1, message = FALSE}
homicide_dat <-
  read_csv('https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv') %>% 
  mutate(reported_date = ymd(reported_date), 
         city_state = paste(city, state, sep = ', '))
#Create tidy dataframe  
homicide_df <-  homicide_dat %>% 
    mutate(case_open = ifelse(disposition != 'Closed by arrest', 1, 0)) %>% 
    add_count(city_state) %>% 
    group_by(city_state) %>% 
    mutate(unsolved_case = sum(case_open)) %>% 
    filter(case_open == 1 | 
          n == 1) %>% #to account for location with no open case  
    select(city_state, unsolved_case, total = n, ) %>% 
    distinct() %>% 
    mutate(percent_unsolved = round(unsolved_case*100/total),1) %>% 
    select(-`1`)
```

The raw data contains `r nrow(homicide_dat)` homicide cases from `r sort(homicide_dat$reported_date)[1]` to the end of 2017 (`r sort(homicide_dat$reported_date, decreasing = TRUE)[1]`). It is collected from `r length(table(homicide_dat$city_state))` cities and according to this data, `r homicide_dat %>% count(city_state) %>% arrange(desc(n)) %>% top_n(1) %>% select(city_state)` has the highest homicide cases (`r homicide_dat %>% count(city_state) %>% arrange(desc(n)) %>% top_n(1) %>% select(n)`). `r round(sort(prop.table(table(homicide_dat$victim_race)), decreasing = T)[1]*100,1)`% of the victims are `r names(sort(prop.table(table(homicide_dat$victim_race)), decreasing = T)[1])` and `r round(prop.table(table(homicide_dat$victim_sex))[2]*100,1)`% are male. Here is the table showing the total number of homicides and number of unsolved homidicdes by city.

```{r}
    homicide_df %>% kable()
```

```{r prop_test_function}
baltimore <- homicide_df %>% 
  ungroup() %>% 
  filter(city_state == 'Baltimore, MD') %>% 
  select(unsolved_case, total)

#Assign function to tidy data after performing the test,
#And only retain the estimate and CIs
prop.test.tidy <- function(x, y){
  prop.test(x, y) %>% 
  tidy() %>% 
  select(estimate, conf.low, conf.high)
}
result_baltimore <- prop.test.tidy(baltimore$unsolved_case, baltimore$total)
```

Focusing on Baltimore, MD, the proportion of homicides that are unsolved is `r round(result_baltimore$estimate, 2)` (`r round(result_baltimore$conf.low, 2)`, `r round(result_baltimore$conf.high, 2)`).

```{r}
finaldat <- 
  map2(homicide_df$unsolved_case, homicide_df$total, prop.test.tidy) %>%         bind_rows() %>% 
  bind_cols(., homicide_df) %>% 
  select(city_state, everything()) 

```

A plot that shows the estimates and CIs for each city

```{r figure}
finaldat %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_bar(stat = 'identity', color = 'violet',
           position = position_dodge()) +
  geom_errorbar(aes( ymin = conf.low, ymax = conf.high), width = .1,
                position = position_dodge(0.9)) +
  ylab('Proportion of unsolved crime') +
  theme(axis.text.x = element_text(color = "blue", size = 8, angle = 90)) 
```

Chicago not only has the highest crime rate but also the highest unsolved crime in the dataset.